---
output:
  html_document: default
  pdf_document: default
---


<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

# Introduction

The goal of this project was to extract the common behavioural patterns of bees in an experiment which shared similarities to the morris water maze experiment. Cluster analysis has previously been successfully applied to the morris water maze experiment to provide insight into how rodents behaviour at a fine grain resolution. The goal of this project was to investigate whether similar techniques were generalizable to slightly different experiments and other species. More specifically to analyse the behaviour of bees being studies using an experiment which is an adaption of the detour paradigm.

In this experiment bees were placed in a circular arena in which they could only move in the x and y directions, i.e. not vertically. Lights were then switched off and on at different positions along the edge of the arena. The bee's position was tracked for the duration of the experiment, producing a dataset of x, y coordinates at uniform time intervals. The experiments were conducted for 3 different treatment groups (1) a no treatment group (2) a saline treatment group and (3) a procaine treatment group.

# Feature Extraction

One of the central challenges of this project was to extract features from the recorded x,y coordinates of the bees so that the data could be represented in a format that would enable typical behaviours and strategies to be detected using cluster analysis. Features were selected that were likely to capture the geometric and positional characteristics of a segment.

##Features
###Median distance from the centre
This is the median Euclidean distance of all points of a segment scaled by the arena radius

###Interquartile range of the distance from the centre
This is the difference between upper and lower quartile distances from the centre scaled by the arena radius

###Focus
The focus is specified as:
$$f=1-\frac{4A}{\Pi d^2}$$
Where A is minimum enclosing ellipsoid around the segment and d is the segment length.

###Eccentricity
The eccentricity is specified as:

E=1-b^2/a^2 
$$E=1-\frac{b^2}{a^2}$$
Where a and b is semi-major axis and the semi-minor axis of the enclosing ellipse.

###Inner radius variation
The inner radius variation is specified as:
$$ v = \frac{(c_{UQ}-c_{LQ})}{c_{MED}} $$
Where $c_{UQ}$, $c_{LQ}$ and $c_{MED}$  are the upper quartile, lower quartile and median for the distance from the centre of the minimum enclosing ellipse.

###Central displacement
The central displacement is specified as the distance between the centre of the arena and the centre of the minimum enclosing ellipse.

###Path efficiency
The path efficiency is specified as:
$$P=\frac{\sqrt{(x_n-x_1)^2+(y_n-y_1)^2}}{\sum^n_{i=1}\sqrt{(x_{i+1}-x_i)^2+(y_{i+1}-y_i)^2}}$$
Where $x_i$ and $y_i$ are ith x and y coordinates of the segment respectively and n is the number of points in the segment.
intuitively, it can be thought of as how directly the segment moves from one location to another. 
(https://www.sciencedirect.com/science/article/pii/S0889159115300398)

###Sum of absolute angles
The sum of absolute angles is specified as:
$$S=\sum\arccos\left(\frac{\langle{\bar{u}},\bar{v} \rangle}{||\bar{u}||.||\bar{v}||}\right)$$
Where $\bar{u}$ and $\bar{v}$ are sequential vectors. (https://www.sciencedirect.com/science/article/pii/S0889159115300398)

## Intermediate calculations
###Calculating the position of the centre of the arena
The centre of the arena was taken to be the midpoint between the max and min x and y coordinates in the entire dataset of points.

### Calculating the diameter of the arena
The diameter of the arena was taken to be either the distance between the max and min Y coordinate or the max and min X coordinate, whichever was the greatest.

###Determining the minimum enclosing ellipse
The minimum enclosing ellipse was computed using the Khachiyan Algorithm. Code from https://ecogenomics.github.io/GroopM/dev_docs/groopm.ellipsoid.EllipsoidTool-class.html was used with some modifications to work for 2d data.

## Session information

<!-- Insert the session information into the document -->
```{r session-info}

```
