---
title: "Introduction"
author: "Mark Platts"
date: 2018-03-03
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

# Project goal

The goal of this project was to extract the common behavioural patterns of bees in an experiment which shared similarities to the morris water maze experiment. Cluster analysis has previously been applied successfully to the morris water maze experiment to provide insight into how rodents behave at a fine grain resolution. The goal of this project was to investigate whether similar techniques were generalizable to different experiments and  species. In particular we wanted to analyse the behaviour of bees in an experiment adapted from the detour paradigm.

# The adapted detour paradigm experiment 

In this experiment bees were placed in a circular arena in which they could only move in the x and y directions, but not vertically. Lights were then switched off and on at different positions along the edge of the arena. The bee's position was tracked for the duration of the experiment, producing a dataset of x, y coordinates at uniform time intervals. The experiments were conducted for 3 different treatment groups (1) no treatment (2) treated with saline (3) treated with saline.

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
