---
title: "Methods"
author: "Mark Platts"
date: 2018-03-03
output: html_document
bibliography: bibliography.bibtex
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

```{r, echo = F}
library(here)
library(dplyr)
library(ggplot2)
library(captioner)
source("https://raw.githubusercontent.com/MarkPlatts/Bee_Behaviour_Cluster_Analysis/master/src/R/helper_functions.R")
```
```{r}
fig_nums <- captioner()

```


# Feature extraction

One of the central challenges of this project was to extract features from the bees recorded x,y coordinates, representing the data in a format that would enable typical behaviours to be detected using cluster analysis. Features were selected that were likely to capture the geometric and positional characteristics of a segment.

##Features

###Median distance from the centre
This is the median Euclidean distance of a segment's points from the centre of the arena scaled by the arena radius [@tiagogehringetal2015-bibtexing].

###Interquartile range of the distance from the centre
This is the difference between upper and lower quartile distances from the centre scaled by the arena radius [@tiagogehringetal2015-bibtexing].

###Focus
The focus is specified as:
$$f=1-\frac{4A}{\Pi d^2}$$
Where A is minimum enclosing ellipsoid around the segment and d is the segment length [@tiagogehringetal2015-bibtexing].

###Eccentricity
The eccentricity is specified as:

E=1-b^2/a^2 
$$E=1-\frac{b^2}{a^2}$$
Where a and b is semi-major axis and the semi-minor axis of the enclosing ellipse [@tiagogehringetal2015-bibtexing].

###Inner radius variation
The inner radius variation is specified as:
$$ v = \frac{(c_{UQ}-c_{LQ})}{c_{MED}} $$
Where $c_{UQ}$, $c_{LQ}$ and $c_{MED}$  are the upper quartile, lower quartile and median for the distance from the centre of the minimum enclosing ellipse [@tiagogehringetal2015-bibtexing].

###Central displacement
The central displacement is specified as the distance between the centre of the arena and the centre of the minimum enclosing ellipse [@tiagogehringetal2015-bibtexing].

###Path efficiency
The path efficiency is specified as:
$$P=\frac{\sqrt{(x_n-x_1)^2+(y_n-y_1)^2}}{\sum^n_{i=1}\sqrt{(x_{i+1}-x_i)^2+(y_{i+1}-y_i)^2}}$$
Where $x_i$ and $y_i$ are ith x and y coordinates of the segment respectively and n is the number of points in the segment.
intuitively, it can be thought of as how directly the segment moves from one location to another [@ILLOUZ2016132].

###Sum of absolute angles
The sum of absolute angles is specified as:
$$S=\sum\arccos\left(\frac{\langle{\bar{u}},\bar{v} \rangle}{||\bar{u}||.||\bar{v}||}\right)$$
Where $\bar{u}$ and $\bar{v}$ are sequential vectors [@ILLOUZ2016132].

## Intermediate calculations
###Calculating the position of the centre of the arena
The centre of the arena was taken to be the midpoint between the max and min x and y coordinates in the entire dataset of points.

### Calculating the diameter of the arena
The diameter of the arena was taken to be either the distance between the max and min Y coordinate or the max and min X coordinate, whichever was the greatest.

###Determining the minimum enclosing ellipse
The minimum enclosing ellipse was computed using the Khachiyan Algorithm. Code from https://ecogenomics.github.io/GroopM/dev_docs/groopm.ellipsoid.EllipsoidTool-class.html was used with some modifications to work for 2d data.

# Segmenting the bees path

A bee's path is defined as he entire path from beginning to end for a single instance of the experiment (`r fig_nums("full_path", display = "cite")`).
```{r, echo = F, cache=TRUE}
df_xy <- read.csv(here::here("data/length100/segment_xys.csv"))
arena_coordinates <- draw_arena(xy = df_xy)
```

```{r, echo = F, fig.width=4, fig.height=5}
df_first_path <- df_xy[df_xy$FileName == "2015-07-14-Sequence-CX-10-03", ]
ggplot(data = droplevels(df_first_path), aes(x_mm, y_mm)) + 
              geom_path() + 
              coord_cartesian(xlim = c(80,240), ylim = c(0,200)) +
              list(geom_path(data = arena_coordinates, aes_string(x = "x", y = "y"))) + 
              theme(text = element_text(size = 6)) + theme(legend.position="none")
fig_nums("full_path", "The full path of a bee in a single experiment.", display = F)
```
`r fig_nums("full_path")`

This was split up into segments of a uniform length where each consecutive segment overlapped the previous segment by 70% of its length. `r fig_nums("three_segments_overlapping", display = "cite")` shows 3 overlapping segments and `r fig_nums("three_segments_separately", display = "cite")` displays these 3 segments separately.

```{r, echo = F, fig.width=4, fig.height=5}
segID3 <- unique(df_xy$SegmentID)[1:3]

df_seg3 <- dplyr::filter(.data = df_xy, SegmentID %in% segID3)

#get rid of duplicates so that there is no overlap but instead on continuous path
df_uniq <- df_seg3[!duplicated(df_seg3[c("x_mm", "y_mm")]),]

df_uniq <- droplevels(df_uniq)

ggplot(data = df_uniq, aes(x_mm, y_mm)) +
              geom_path() +
              coord_cartesian(xlim = c(80,240), ylim = c(0,200)) +
              list(geom_path(data = arena_coordinates, aes_string(x = "x", y = "y"))) +
              theme(text = element_text(size = 6))
fig_nums("three_segments_overlapping", "Three overlapping segments from the full bee's path.", display = F)
```
`r fig_nums("three_segments_overlapping")`

```{r, echo = FALSE, fig.height=2.5, fig.width=6}
ggplot(data = df_seg3, aes(x_mm, y_mm)) +
              geom_path() +
              coord_cartesian(xlim = c(80,240), ylim = c(0,200)) +
              list(geom_path(data = arena_coordinates, aes_string(x = "x", y = "y"))) +
              theme(text = element_text(size = 6)) +
              facet_grid(.~SegmentID)
fig_nums("three_segments_separately", "Three segments displayed separetely.", display = F)
```
`r fig_nums("three_segments_separately")`

# Majority voting

Since segments overlapped it was necessary to resolve the issue where overlapping segments belonged to different clusters. We used a majority voting approach similar to the one used in [2017arXiv171107446V], but without using weights since we do not know the classes. K-means cluster analysis was performed to find the natural groupings of segments according to the above extracted features. For each point a vote was taken from each segment that overlapped that position and the point assigned to the cluster with the most votes. Points where two or more cluster groups tied, were considered unidentified. 

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```

# References
